Social Housing in Toronto

### 2024-04-21 paper/paper.qmd
commit

# Create a data frame
plot_data <- data.frame(Year_Quarter = year_quarter,
                        Household_no_dependents = household_no_dependents,
                        Household_with_dependents = household_with_dependents)

@@

# Create a line plot
ggplot(plot_data, aes(x = Year_Quarter)) +
  geom_line(aes(y = Household_no_dependents, color = "Household without Dependents"), size = 1.2) +
  geom_line(aes(y = Household_with_dependents, color = "Household with Dependents"), linetype = "dashed", size = 1.2) +
  scale_color_manual(values = c("blue", "red")) +
  labs(title = "Households with and without Dependents Applying for Social Housing",
       x = "Year Quarter",
       y = "Application Numbers") +
  theme_minimal() +
  theme(legend.title = element_blank())

>>>>

# Create a data frame
plot_data <- data.frame(Year_Quarter = year_quarter,
                        household_no_dependents = household_no_dependents,
                        household_with_dependents = household_with_dependents)

@@

# Create a line plot
ggplot(plot_data, aes(x = Year_Quarter)) +
  geom_line(aes(y = household_no_dependents, color = "Household without Dependents"), size = 1.2) +
  geom_line(aes(y = household_with_dependents, color = "Household with Dependents"), linetype = "dashed", size = 1.2) +
  scale_color_manual(values = c("blue", "red")) +
  labs(title = "Households with and without Dependents Applying for Social Housing",
       x = "Year Quarter",
       y = "Application Numbers") +
  theme_minimal() +
  theme(legend.title = element_blank())
